Semi-supervised low-rank logistic regression for high-dimensional neuroimaging data

### 2015-05-30 paper_nips/paper.tex
suggest to remove bioinformatics tag
suggest BOLD signal variation instead of BOLD signal

\textbf{keywords}: dimensionality reduction; semi-supervised learning;
bioinformatics; fMRI; systems neuroscience

@@

\section{Introduction}
%
Methods for neuroimaging research can be grouped by discovering
neurobiological structure or assessing the neural correlates associated
with mental tasks.
To discover, on the one hand, spatial distributions of neural activity
structure across time,
independent component analysis (ICA) \cite{beckmann2005} is often used.
It decomposes the BOLD (blood-oxygen level-dependent) signals into the
primary modes of variation.
The ensuing spatial activity patterns are believed to represent
brain networks of
functionally interacting regions \cite{smith2009}.
Similarly, sparse principal component analysis (SPCA) \cite{varoqu2011}
has been used to
separate BOLD signals into parsimonious network components.
Thus extracted brain networks are probably
manifestations of electrophysiological oscillation frequencies \cite{hipp15}.
Their fundamental organizational role is further
attested by continued covariation during sleep and anesthesia \cite{fox07}.
%
Network discovery by applying ICA or SPCA is typically performed on
task-unrelated (i.e., \textit{unlabeled}) ``resting-state'' data.
These capture brain dynamics
during ongoing random thought without controlled environmental stimulation.
In fact, a large proportion of the BOLD signal is known
not to correlate with a particular behavior, stimulus, or experimental task
\cite{fox07}.

>>>>

% XXX Michael: Suggesting removal of bioinformatics tag,
% XXX see http://en.wikipedia.org/wiki/Bioinformatics
\textbf{keywords}: dimensionality reduction; semi-supervised learning;
\suggestremove{bioinformatics;} fMRI; systems neuroscience

@@

\section{Introduction}
%
Methods for neuroimaging research can be grouped by discovering
neurobiological structure or assessing the neural correlates associated
with mental tasks.
To discover, on the one hand, spatial distributions of neural activity
structure across time,
independent component analysis (ICA) \cite{beckmann2005} is often used.
It decomposes the BOLD (blood-oxygen level-dependent) signals into the
primary modes of variation.
The ensuing spatial activity patterns are believed to represent
brain networks of
functionally interacting regions \cite{smith2009}.
Similarly, sparse principal component analysis (SPCA) \cite{varoqu2011}
has been used to
separate BOLD signals into parsimonious network components.
Thus extracted brain networks are probably
manifestations of electrophysiological oscillation frequencies \cite{hipp15}.
Their fundamental organizational role is further
attested by continued covariation during sleep and anesthesia \cite{fox07}.
%
Network discovery by applying ICA or SPCA is typically performed on
task-unrelated (i.e., \textit{unlabeled}) ``resting-state'' data.
These capture brain dynamics
during ongoing random thought without controlled environmental stimulation.
% XXX Michael: Added variation/variance, because otherwise that is trivial:
In fact, a large proportion of the BOLD signal \suggestadd{variation} is 
known
not to correlate with a particular behavior, stimulus, or experimental task
\cite{fox07}.
